\documentclass[11pt]{article}
\usepackage{graphicx}
\setlength{\parindent}{0pt}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
% Với XeLaTeX + tiếng Việt, bạn có thể đổi inputenc/fontenc/babel sang fontspec+polyglossia
% nhưng để giữ nguyên theo template gốc:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.5cm,top=2cm,right=1.5cm,bottom=2cm]{geometry}

% by: Aline R. Antunes (nguyên bản); tham số hoá bởi bạn.

\begin{document}

% =========================
% Header (Name)
% =========================
\begin{center}
    \textbf{Blu e's}\\
    \hrulefill
\end{center}

% =========================
% Contact line
% =========================
\begin{center}
    Anytown, USA \textbullet{} Anytown, USA \textbullet{} \href{mailto:blue.es@example.com}blue.es@example.com \textbullet{} (555) 123-4567
\end{center}

\vspace{0.5pt}

% =========================
% Professional Summary
% =========================
\begin{center}
    \textbf{Professional Summary}
\end{center}

\vspace{6pt}

AI Application Engineer with expertise in applying AI principles to develop LLMs, NLP solutions, and RAG systems. Specialized in model families such as GPT, Claude, Gemini, Mistral, and Llama, alongside DevOps and cloud technologies like AWS, Docker, and CI/CD pipelines. Seeking to leverage expertise in AI and cloud technologies to drive innovative AI application development at We are seeking a talented Al Application Engineer.

\vspace{12pt}

% =========================
% Education
% =========================
\begin{center}
    \textbf{Education}
\end{center}

\textbf{University of California, Berkeley} \hfill Berkeley, CA

Master of Science, Computer Science. GPA: 3.9/4.0 \hfill May 2020
Relevant Coursework: Artificial Intelligence, Natural Language Processing, Machine Learning, Deep Learning; Awards: Dean's List, Outstanding Graduate Student Award
\vspace{12pt}



% =========================
% Experience
% =========================
\begin{center}
    \textbf{Experience}
\end{center}

\textbf{Example Corp} \hfill Anytown, USA\\
\textbf{AI Application Engineer} \hfill Jan 2022 -- Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Developed and deployed a chatbot application using GPT-3.5, resulting in a 30% reduction in customer support tickets.
    \item Implemented a RAG (Retrieval-Augmented Generation) system leveraging Llama 2 for enhanced knowledge retrieval and response generation, improving response accuracy by 25%.
    \item Managed and maintained CI/CD pipelines for AI application deployment on AWS, ensuring continuous integration and delivery of new features and updates.
    \item Utilized Docker and containerization technologies to ensure consistent and scalable deployment of AI models and applications across different environments.
\end{itemize}

\vspace{12pt}
\textbf{Data Solutions Inc.} \hfill Anytown, USA\\
\textbf{NLP Engineer} \hfill June 2020 -- Dec 2021
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Developed and optimized NLP pipelines for sentiment analysis and text classification using Python and TensorFlow, achieving a 90% accuracy rate.
    \item Experimented with various LLMs including Claude and Gemini to identify optimal models for specific NLP tasks, leading to improved performance and efficiency.
    \item Collaborated with cross-functional teams to integrate NLP solutions into existing products, enhancing user experience and data-driven decision-making.
\end{itemize}

\vspace{12pt}

% =========================
% Leadership & Activities
% =========================

% =========================
% Skills & Interests
% =========================
\begin{center}
    \textbf{Skills \& Interests}
\end{center}

\textbf{Technical:} Large Language Models (LLMs): GPT, Claude, Gemini, Mistral, Llama, Natural Language Processing (NLP), Retrieval-Augmented Generation (RAG), Artificial Intelligence (AI), AWS, Docker, CI/CD Pipelines, Python, TensorFlow, PyTorch\\

\textbf{Language:} English (Native)\\


\textbf{Interests:} AI Research, Open Source Projects, Machine Learning Applications


\end{document}